---
title: |
 **Estimating Agricultural Practices and their Impact on Biodiversity from Agricultural Statistics: A Proof-of-Concept Study on Food Labels in France**
author: "Sarah HUET, Clélia SIRAMI, Abdoul DIALLO, Julie REGOLO, Valentin BELLASSEN"
#date: "`r format(Sys.time(), '%B %d, %Y')`"
date: "2024-08-26"
format:
 docx:
  reference-doc: custom-reference-doc.docx
bibliography: references.bib
editor_options: 
 chunk_output_type: console
---

# Abstract

-   Our method, BVIAS (Biodiversity Value Increment from Agricultural Statistics):
    -   objective, robust and operational to estimate agricultural practices and calculate their impact on biodiversity, at the workshop level in a representative sample of French farms
    -   Preliminary assessment of the impact of 25 labelled products on biodiversity.
-   Cultural practices in Large crops: only organic stands out from conventional
    -   Nitrogen fertilization: 100% mineral fertilizer in less but 5 times more organic fertilization which leads to a total fertilization in kg N/ ha similar to conventional
    -   Plant protection products: \>96% less phyto on field crops
-   Dairy farming practices: only the organic and PDO of Franche-Comté stand out
    -   Organic: Share of areas in temporary grassland \> 2 times larger than for conventional grassland, but significant differences on permanent grassland
    -   Comté:
        -   1.2 times more permanent grassland than the average France of the conventionals
        -   Compared to conventional Franche-Comté in the mountain area, only the share of temporary grassland differs: share of surface \> 2 times larger
-   The different practices of Organic and County lead to a lower impact per hectare but also to lower yield where an impact similar to the kilo (cf. figure)
-   The estimated practices are consistent with the requirements of the specifications, and only specifications with specific constraints to limit the impact of productions (i.e. organic farming and county) are associated with less impacting practices than conventional ones.
-   Limiting the use of plant protection products on crop production and increasing the proportion of grassland used for livestock farming reduces the impact per hectare of the products on biodiversity but tends to reduce yields, compensating for differences in impact per kilo.
-   Here, only three crop practices are estimated (tillage, quantity of nitrogen fertilization, phyto-product loading). However, before informing the environmental display, landscape effects of agroecological infrastructure, crop heterogeneity and organic/mineral fertilization share must be included in the BVIAS model

# Introduction

Biodiversity erosion is probably the most important environmental crisis with climate change. While the impacts of current climate change trajectories are estimated at several tens of percentage points of GDP (Rose et al., 2022), the only pollinator loss is 1-2% of GDP, and about €4 billion for a country like Germany</b> (Lippert et al., 2021). The IPBES groups and prioritizes five determinants of biodiversity loss (IPBES, 2019) : land use (30%), direct exploitation (23%), climate change (14%), pollution (14%) and invasive species (11%). Agriculture is mainly involved in three of these five determinants (land use, climate change and pollution), and is, with direct exploitation, one of the two main economic sectors responsible for the global erosion of biodiversity (Maxwell et al., 2016; Tilman et al., 2017).

Environmental labelling on agricultural products is one of the policies that could reduce the impact of agriculture on biodiversity. Although consumer information appears to trigger only small short-term changes in food choices (De Marchi et al., 2023; Dubois et al., 2021), environmental signage opens the way to several indirect long-term effects. It encourages producers to change their practices, and processors to change product formulations to improve their ratings, and can be used as a support for other policies (e.g. minimum rating requirement for public order, tax based on rating, ...).

At the European level, the Commission published a proposal for a regulation in March 2023 requiring all companies wishing to claim an environmental better-performing to use the life cycle analysis framework, and for example the EU Product and Organisation Environmental Footprint (PEF and PEO) method, to objectify the claim. France has taken a further step with the 2021 Climate and Resilience Act, which plans to make environmental labelling mandatory on all food products after an experiment scheduled to last for 5 years. Following the proposal of Ecoscore by ADEME, which should inspire the future government tool, several stakeholders reproach it for limiting itself to the analysis of the life cycle of products (Interbev, 2024) . Their main argument is that life cycle analysis fails to account for the impact of food products on biodiversity. The Scientific Council for Experimentation notes that life cycle analysis does address three of the five main determinants of biodiversity loss, but recognizes the value of complementing life cycle analysis on some points (Soler et al., 2021). In view of this controversy, it is urgent to propose an objective, robust and operational method for calculating the impact of food products on biodiversity. This is what this section is about.

We (@com1) believe that the environmental display should be based on a biodiversity indicator that meets five key requirements (@tab-1):

-   *An explicit and operational definition of biodiversity.* The term biodiversity is very polysemous. For this reason, it is important to explain an operational definition adapted to the context (Santana, 2014). This definition must also keep an intuitive link with the main issues related to biodiversity erosion such as loss of species or ecosystems (and especially those that provide important services such as pollinators).

-   *Addressing the main determinants of biodiversity loss related to agriculture*, namely land use, climate change and pollution.

-   *Rely on data of biodiversity or practices that are measured and representative at the plot level* to estimate an impact of actual rather than potential practices on biodiversity.

-   *Allow for evaluation of any food product.* The environmental labelling must be made mandatory and must be applicable to any product based on currently available data, differentiating both different products (e.g. lentils versus chicken) and different production modes of the same product (e.g. conventional versus organic wheat).

-   *Rely on a validation of the estimated impact based on in situ biodiversity measurements.* There are always two ways to assess an impact: in situ measurement and modelling. In the second case, an essential criterion of robustness is the validation of the model, at least on predicted variables for which in situ measurements of biodiversity are available (e.g. biodiversity per unit area).

***The literature review in chapter 2*** shows that three main types of methods for assessing the impact of food products on biodiversity can be distinguished: in situ observations of biodiversity by species counting in ecosystems, modelling the impact of agricultural practices on biodiversity, and modelling the impact of label specifications on biodiversity. The adequacy of these three methods with the requirements of environmental display is summarized in the following three paragraphs and summarized in @tab-1.

*In situ observations* clearly meet the data and validation criteria. However, they are punctual in both space and time, making it difficult to estimate all food products. With a considerable effort, the most comprehensive meta-analyses in terms of taxa studied allow an average effect to be estimated by type of product and by differentiating some production modes. Tuck et al. (2014) distinguishes between organic and conventional agriculture for five agrosystems, and estimates that the specific diversity is on average 30% higher in organic farming. Specific diversity is a relatively explicit definition of biodiversity and has an intuitive link with the main issues related to biodiversity erosion as long as one remains within the same agro-system. This link is however less than true when comparing different ecosystems or agrosystems because we are then comparing completely different species groups (Santana, 2014; Sarkar, 2002). Finally, in situ observations have the major disadvantage of not taking into account the amount of anthropogenic surface. The measure of biodiversity is expressed per unit area in these studies, so it attributes the same impact to two identical productions (e.g. wheat), even if one occupies twice as much area as the other. This is a paradox that is difficult to manage in an environmental display because two tons of wheat have the same impact as one tonne of wheat, provided the amount of inputs per hectare is the same.

*Modelling based on agricultural practices data* is the method used in life cycle analyses. Crenna et al. (2019) shows that the impact on biodiversity in the EU food system is mainly caused by animal products (70-75% of the total impact), and more specifically by pork (19-23%) and beef (21-25%). Read et al. (2022) shows that the risk of species extinction caused by American food consumption could be reduced by 30% by adopting the EAT-Lancet flexitarian diet</b> (Willett et al., 2019), and up to 45% by reducing waste. The models used in these studies (e.g., Chaudhary et al., 2015; ReCiPe, see Curran et al., 2014; of Baan et al., 2013) however take into account differences in practices within the same production only frustratingly (typically by three levels of «intensity», without taking into account the landscape effects related to agroecological infrastructures, the size of the plots,... ). This results in very low sensitivity to differences in practices per unit area (Wermeille et al., 2024). To remedy this, Lindner et al. (2019) propose a model that takes into account 14 agricultural practices in addition to the type of agrosystem (prairie vs culture vs forest). Using a simplified version to fit the data limits of the Agribalyse life cycle inventory database, Lindner et al. (2022) concludes that organic farming reduces the biodiversity impact of the kilogram of wheat (-33%) or the litre of milk (-27%), but increases the value of the kilogram of chicken (+33%). In all cases, the predictions of these models are not or only little validated by comparing them with in situ observations of biodiversity.

*Modelling from specifications*, for the moment confined to grey literature, offers an assessment of the potential impact of restrictions placed in the specifications of labels. Alliot et al. (2021) conclude that the specifications associated with organic farming (AB, Demeter, Nature and Progrès) strongly limit the damage to biodiversity (score between 3/5 and 4/5), that the AOP Comté and Bleu Blanc Cœur limit them moderately (2/5) and that the other labels (HVE, Zero Pesticides, Label Rouge,...) do not limit them. This approach has the advantage of being applicable to any label, but ignores the actual practices implemented. For example, the county’s specifications that limit mineral fertilization to 50 kgN ha-1 do not allow the quantities actually used to be known, nor, a fortiori, the possible effects on greater cultural diversity or on the ratio between organic and mineral nitrogen. Moreover, this approach suffers from the same limitation as in situ observations on the non-consideration of land tenure and the same limitation as other models on the absence of validation.

see @tbl-methods

```{r echo=FALSE,include=FALSE}
library(gt)
library(dplyr)

```

```{r echo=FALSE,include=TRUE}
#| label: tbl-methods
#| tbl-cap: "**Environmental Labeling Requirements and Existing Methods.** The colour code gives the authors' judgement on the degree of adequacy of the type of method with each criterion (requirement [fulfilled]{style=color:#99CC99;}, [partially fulfilled]{style=color:#FFCC99;} or [not fulfilled]{style=color:#FF9999;}), based on the example cited at the top of the table."


tmp_table <- data.frame(
 x1= c(
   "",
   "Explicit and operational definition of biodiversity",
   "Addressing the main determinants of biodiversity loss related to agriculture",
   "Land use",
   "Climate change",
   "Pollution",
   "Based on measured data, biodiversity or practices at the farm level",
   "Allow a default estimate on any food product",
   "Validation based on biodiversity measurements"
   ),
 x2 = c(   
   "In situ observations (e.g., Tuck et al., 2014)",
   "Specific diversity (other studies present a plurality of indicators including abundance, diversity, presence of rare/endemic species,...).No systematic link with the sixth extinction crisis.",
   "",
   "Consideration of landscape effects. No consideration of yields",
   "Not taken into account",
   "Taking into account all pollution",
   "Yes (biodiversity), but without guarantee on the representativeness of the plots (sample size often small, difficulty in covering all productions)",
   "No (too few measurements to differentiate each product)",
   "Yes (intrinsically)"
   ),
 x3 = c(
   "Modelling from agricultural practices data (e.g. Lindner and Koch, 2022)",
   "Degradation of natural state (or risk of extinction of species for other studies)",
   "",
   "No account taken of landscape effects. Consideration of yields",
   "Not considered by Lindner et al. (2022), but considered by other models",
   "Taking into account the main pollutions without effect size",
   "Yes (practices), but often incomplete and without representativeness assurance (life cycle inventories)",
   "Differentiates the main products, and the organic label",
   "No"
   ),
 x4 = c(
   "Modelling from specifications (e.g. Alliot et al., 2021) ",
   "Implied definition",
   "",
   "Consideration of landscape effects. No consideration of yields",
   "Not taken into account",
   "Taking into account the main pollutions without effect size",
   "No (specification)",
   "Differentiates many labels, but not products between them",
   "No"
   ),
 x5 = c(
   "BVI AD (this study)",
   "Degradation of natural state",
   "",
   "Consideration of landscape effects and yields",
   "Not taken into account",
   "Taking into account the main pollutions with effect size",
   "Yes (practices, sample provided and representative: FADN, AC, LPIS)",
   "Differentiates the main products, and labels sufficiently represented",
   "Yes (consensus orders of magnitude in the literature)"
   )
 ) %>%
  # add columns for color
  mutate(
    #col1 = c(0,0,0,0,0,0,0,0),
    col2 = c(0,2,0,2,1,3,3,1,3),
    col3 = c(0,3,0,2,2,2,2,3,1),
    col4 = c(0,2,0,2,1,2,1,2,1),
    col5 = c(0,3,0,3,1,3,3,3,3)
  )

tmp_palette = c("#FF9999","#FFCC99", "#99CC99")

tmp_table %>%
 gt() %>%
    data_color(   columns = col2,
                  target_columns = x2,
                  rows = col2 >0,
                method = "numeric",
                  palette = tmp_palette,
                domain = c(1,3)
    ) %>% 
    data_color(   columns = col3,
                  target_columns = x3,
                  rows = col3 >0,
                method = "numeric",
                  palette = tmp_palette,
                domain = c(1,3)
    ) %>% 
    data_color(   columns = col4,
                  target_columns =x4,
                  rows = col4 >0,
                method = "numeric",
                  palette = tmp_palette,
                domain = c(1,3)
    ) %>% 
    data_color(   columns = col5,
                  target_columns = x5,
                  rows = col5 >0,
                method = "numeric",
                  palette = tmp_palette,
                domain = c(1,3)
    ) %>% 
  cols_hide(col2:col5)



#rm(tmp_table)

```

Finally, for the three families of methods, it is now difficult to judge the representativeness of the results proposed for a given product type or label. In situ measurements, such as life cycle surveys, are generally carried out on a limited number of farms without any explicit indication of their representativeness. This limit may become even more critical as the pressure of environmental labelling may lead technical institutes, leading providers of life cycle inventories, to choose examples that are flattering for their sector. The increasing availability of data collected for public statistics and agricultural policies now allows this risk to be avoided and the sample sizes increased tenfold. Some studies have already linked data from the Agricultural Accountancy Data Network (FADN) and the National Institute of Origin and Quality (INAO) to assess the effectiveness of labelled farms. Jeanneaux et al. (2018) shows that some label sectors do not generate better profitability, because the premium product is fully compensated by a lower technical efficiency (e.g. Label Rouge or AB meat poultry). Sengel et al. (2022) estimates that dairy farms under geographical indications generate 30% higher income per unit of work than conventional farms. This difference, mainly due to the names of the Comtoises, rises to 40% after restriction of comparison to farms with comparable structure and location, following a «matching» procedure.

Our study proposes an objective, robust and operational method to calculate the impact of food products on biodiversity. This method is applied to the main French agricultural productions, distinguishing the main traceable labels for an environmental display (organic farming, red label and geographical indications). It is modelled on the BVI model (Lindner et al., 2019), but allows for the three main limitations raised when applying it to environmental signage (Lindner and Koch, 2022). By relying on agricultural statistics (e.g. FADN, Recensement Agricole), it has access to important sample sizes and operating characteristics that make it possible to objectify the choice of counterfactual to label holdings, following a “matching” procedure. By mobilizing the maps of the plot (Register plot graphic or RPG) and tree elements (BD Haies), it allows to take into account the landscape effects. Finally, by validating predicted differences in impacts against the orders of magnitude established from in situ measurements of biodiversity in the literature, it strengthens confidence in the robustness of estimated impacts.

# Modelling the impact of crop practices on biodiversity

## The BVI model

The model chosen to estimate the impact of cultural practices on biodiversity is the BVI model as originally selected by ADEME for environmental display (Lindner 2022). This model considers biodiversity at the level of the plot and adjacent semi-natural spaces (NSS), and takes into account land use (grassland versus crop), landscape effects and intensity of cropping practices. We estimate seven different parameters with a major impact on biodiversity within each land use category: tillage, application of nitrogen fertilizers (quantity and quality), use of plant protection agents, density of hedges, the size of agricultural parcels and cultural diversity.

The BVI method introduces a standard biodiversity value with an emphasis on a naturalness objective. To aggregate the impact of these practices on this biodiversity standard and include them as input parameters for the BVI model (Lindner 2022), their intensity values are normalized in the interval [0.1], the minimum intensity corresponding to 0 and the maximum corresponding to 1. In order to exclude possible outliers, the 95th percentile of positive values is set as a threshold from which values are normalized to 1. The contribution to the biodiversity value of each practice is calculated by applying a function specific to each parameter (@lindner_valuing_2019, @lindner_bringing_2022; @eq-1).

$$
BVC_{i,l,v}= \gamma_{l,v} + \epsilon_{l,v} \cdot \exp(- \frac{ |(x_{i,l,v}^{\delta_{l,v}} - \beta_{l,v}) ^{\alpha_{l,v}}| }{2\sigma_{l,v}^{\alpha_{l,v}}})
$$ {#eq-1}

where $BVC$ is the biodiversity value contribution (without dimension, 1 = maximum contribution of practice, 0 = minimum contribution) of a practice $v$ for each observation $i$ in a land use type $l$, $x$ is the normalized practice intensity, and $[\alpha,\beta,\delta,\epsilon,\gamma,\sigma]$ are function constants.

The average of these contributions provides the land use specific biodiversity value ($BV_{LU}$). To take into account that biodiversity levels are on average higher in grasslands than in crops, $BV_{LU}$ is then projected into the range of possible biodiversity for the land use type (i.e., crop or grassland), in order to obtain a standardized biodiversity value ($BV_{norm}$). A function is then applied to this normalized value to obtain the local biodiversity value ($BV_{loc}$, Equation 4.). The latter function aims to maximize the difference between the most anthropogenic land uses and, conversely, minimize the difference between the most natural land uses. For example, biodiversity is modeled as 1.5 times higher in the most intensive grassland ($BV_{loc}$ = 0.754) than in the most intensive crop ($BV_{loc}$ = 0.500).

$$
BV_{loc,i} = 1.017626088 \cdot (1 - \exp( -4.055847776 \cdot BV_{norm,i}))
$$ {#eq-1}

Finally, the impact on biodiversity value (BVI) of one hectare is defined as BVIha = 1 - BVloc.

## Attribution of biodiversity impact to farm products

To assign the previously calculated hectare impact to different farm products, we follow the common life cycle analysis (LCA) recommendations of restricting the scope when possible and allocating where not (JRC, 2010). Where applicable, we opt for the economic allocation of impact – that is to say in proportion to the turnover generated by each product – which is both the most common choice and the best approximation of the share of responsibility in generating the impact (ref???Hayo).

In the case of crop products, it is possible to narrow the scope, i.e., to relate farm variables to the scale of cultivation to calculate directly the impact of one hectare of crop (see 2.4). The impact on biodiversity of one kilogram of crop production is then simply calculated as: BVIkg = BVIha/ Y where Y is the yield of the crop in kg/ha.






# Comments

::: {#com1}
18/04/24 Clelia: Est-ce que c'est que "nous"? J'avais l'impression qu'il y avait déjà certains critères bien identifiés dans la littérature (point 1 et 2) ou le cahier des charges pour l'affichage environnemental (point 4)

25/04/24 Valentin: Si tu les as sous la main, c’est sûr que c’est mieux, mais pas moi
:::

# References
